Software variability in fMRI analysis:\\ comparing between-tool and numerical errors

### 2021-12-07 paper/paper.tex
Edits throughout

We replicated the fMRI analysis described as study `ds000001'
in~\cite{schonberg2012decreasing}, relying on the data publicly available
in OpenNeuro at \url{https://openneuro.org/datasets/ds000001} and using
three widely-used software packages for fMRI data processing, namely FMRIB
Software Library (FSL)~\cite{jenkinson2012fsl}, Analysis of Functional
NeuroImages (AFNI)~\cite{cox1996afni}, and Statistical Parametric
Mapping (SPM)~\cite{penny2011statistical}. We selected this dataset because
comparable analysis pipelines implemented in FSL, AFNI and SPM were already 
publicly available and extensively described in~\cite{bowring2019exploring}.
Furthermore, the work in~\cite{bowring2019exploring} already evaluated the
effect of tool variability for this dataset, which we intended to
complement with the present quantification of numerical variability.

In the selected study, 16 healthy adult subjects participated in the
balloon analog risk task~\cite{lejuez2002evaluation} to measure risk-taking
behavior over three scanning sessions~\cite{schonberg2012decreasing}. We
reused the preprocessing, first-level, and second-level analyses
implemented by~\cite{bowring2019exploring} consistently across all three
software packages. Table~\ref{table:pipeline-steps} summarizes the analytical steps in each
pipeline.

@@

To introduce numerical noise in the analyses, we used
the Fuzzy Libmath library~\cite{salari2021accurate}, a version of the GNU
mathematical library (libmath) instrumented with Monte-Carlo arithmetic.
Monte-Carlo arithmetic simulates roundoff and catastrophic cancellation
errors by introducing a controlled amount of noise in the floating-point
operations through the following perturbation~\cite{Parker1997-qq}:

@@

Fuzzy Libmath introduces numerical perturbations in the values returned by
mathematical functions but not in their input values or within their
implementation. This is done by wrapping the original functions and
applying function \texttt{inexact} to their returned values.
Listing~\ref{algo:wrapper} shows an example of this wrapping for the
\texttt{log} function in single and double precision. In this wrapper, the
original function is called through \texttt{dlsym}, a function that returns
the memory address of a symbol --- in our case \texttt{RTLD\_NEXT}, the
address of the next occurrence of the function in memory. Function wrappers
are compiled with Verificarlo. Verificarlo instruments the result of the
addition between the original function output and a floating-point zero.

@@

In~\cite{salari2021accurate}, Fuzzy Libmath was shown to accurately
simulate the effect of Linux operating system updates in structural
pre-processing pipelines. To validate our pipeline instrumentations for the present study, we first verified that non-instrumented
executions of the same pipeline on the same dataset led to identical
results. We also listed the pipeline
library dependencies using the \texttt{ldd} Linux utility and verified that
(1) the tested pipelines were dynamically linked to the GNU libmath library, and 
(2) there was no alternative implementation of elementary mathematical functions in the pipeline dependencies.
Finally, we verified that the use of Fuzzy libmath affected computational results.

@@

We measured between-tool (BT) variability by running the pipelines
described in~\cite{bowring2019exploring} with FSL version 5.0.10, AFNI
version 18.1.09, and SPM12 version r7771 executed with GNU/Octave version
5.2. These software versions were identical to the study
in~\cite{bowring2019exploring} except for SPM for which we used GNU/Octave
instead of MATLAB to enable mathematical function instrumentation using
Fuzzy Libmath. Indeed, MATLAB uses its own built-in mathematical functions,
which prevents the use of Fuzzy Libmath. In AFNI, we set the number of
threads to 7 even though AFNI executions
in~\cite{bowring2019exploring} were single-threaded. This was meant to
reduce the time overhead resulting from Fuzzy Libmath instrumentation. All
the analyses were conducted on the CentOS 7.3 operating system. The
computations were performed on \href{https://www.computecanada.ca}{Compute
Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake
@ 2.4 GHz (40 cores/node) CPU and 8~GB of RAM per core. We encapsulated the
above-mentioned software packages in Docker container images available at
\url{https://github.com/big-data-lab-team/fuzzy-neurotools}.

@@

\section{Results}
All scripts and data to reproduce the results are
available in out GitHub repository at \url{https://github.com/big-data-lab-team/fuzzy-neurotools}.

@@

We verified the correctness of our analyses by comparing our unperturbed
t-statistic group maps with the ones obtained
in~\cite{bowring2019exploring}. For FSL, we found
identical checksums. For SPM, the checksums were different but differences
were visually unnoticeable. For AFNI, the activation maps were similar
overall, however, differences were more noticeable visually. 
The observed differences remained small (see Appendix ~\ref{sec:supp-repro}) and might be due to the use of
Octave vs MATLAB in SPM and of multithreading in AFNI. We performed visual quality control of the AFNI
and SPM results for each individual subject and confirmed that T1-weighted images were
correctly skull-stripped and registered to the MNI template.

@@

Table~\ref{table:pipeline-stats} reports on summary statistics for the
group-level t-statistics. For each tool pair (A, B), BT variability was
significantly larger than machine error in tool A or B, in both thresholded
and unthresholded maps (Wilcoxon signed-rank test p~\textless~$10^{-162}$
for all tests, t-test p=0 for all tests). These global differences were
confirmed across the maps (Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B},\textbf{C}). 
In addition, BT and WT variability appeared moderately correlated (Pearson's R
in [0.56, 0.58], p=0.0, Figure~\ref{fig:unthresh-maps}-\textbf{D}). Interestingly, the correlation 
was driven by a set of voxels exhibiting comparable BT and
WT values (located around the identity line in the XY plot), which, however, did not seem to have 
any spatial consistency \tristan{Ali, check for intensity differences between these voxels and the other ones}.

\setlength{\tabcolsep}{5pt}
\begin{table}[h]
    \centering
    \begin{tabular}{cccccc|cc}
        \toprule
        && \multicolumn{4}{c|}{Group analyses} & \multicolumn{2}{c}{Subject analyses}\\
        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded} \\
        % \cmidrule{3-8}
        {} & {} & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ \\
        \midrule
        \rowcolor{lightgray!50}
        {Between Tools} & FSL vs. SPM        &  1.282       & 0.525      & 0.443     & 0.344  & 0.366       & 0.293     \\
        \rowcolor{lightgray!50}
        {(BT)} & FSL vs. AFNI                &  1.548       & 0.616      & 0.547     & 0.441  & 0.439       & 0.352     \\
        \rowcolor{lightgray!50} 
        {} & AFNI vs. SPM                    &  1.475       & 0.672      & 0.608     & 0.477  & 0.491       & 0.381     \\
        {Within Tool} & FSL                  &  0.354       & 0.491      & 0.082     & 0.065  & 0.077       & 0.054     \\
        {(WT)}   & SPM                       &  0.252       & 0.448      & 0.054     & 0.045  & 0.048       & 0.037     \\
        {}   & AFNI                          &  0.434       & 0.524      & 0.128     & 0.135  & 0.108       & 0.131     \\
        \bottomrule
    \end{tabular}
    \caption{Voxel-wise mean and standard deviation of BT and WT variability
    in group and subject t-statistics maps. \tristan{add stats on subject-level thresholded maps}}
    \label{table:pipeline-stats}
\end{table}

@@

  Table~\ref{table:pipeline-stats} also reports on summary statistics for
  subject-level unthresholded t-statistics maps. As for group-level maps,
  BT variability was consistently larger than WT variability (Wilcoxon
  signed-rank test p~\textless~$10^{-160}$ for all tests, t-test p=0 for
  all tests). However, Figure~\ref{fig:unthresh-maps-sbj} shows that for
  some subjects, machine error (WT variability) approached and even
  surpassed BT in some regions. As for the group maps, BT and WT
  variability appeared moderately correlated for all subjects (R in [0.442,
  0.612], p=0.0 for all subjects, see Appendix~\ref{sec:supp-subjects}).

@@

  Figure~\ref{fig:thresh-maps}-\textbf{A},\textbf{B},\textbf{C} compares BT
  and WT for thresholded group maps. Thresholding is an unstable operation
  that introduced variability for both BT and WT at the edges of
  active regions. Except in these regions, BT remained consistently larger
  than WT. To measure correlation between BT and WT, we
  measured WT instability and BT instability in each region of the
  HCP-MMP1.0 parcellation. The confusion matrices in
  Figure~\ref{fig:thresh-maps}-\textbf{D} report on such instabilities for
  the 360 tested regions. The average ratio of unstable regions was 26\%
  for BT and 9.2\% for WT, which confirmed that BT variability was larger than machine error.
  The average Cohen's kappa score\footnote{$\kappa \leq 0$ denotes chance agreement, -1 \textless $\kappa$ \textless 1} between WT instability and BT instability was $\kappa=0.17$, indicating 
  a moderate agreement between WT instability and BT instability.

  %%%%%%%%%% Var. of Thresh %%%%%%%%
  \begin{figure*}[ht]
        \begin{subfigure}[ht]{\textwidth}
          \centering
          \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
          %\caption{Standard deviation of thresholded t-statistics map on template surface}
          \end{subfigure}
        \centering
      \caption{Thresholded group t-statistics standard deviation maps
      computed across tools (\textbf{A}) and Fuzzy Libmath samples
      (\textbf{B}). The confusion matrices of activation instability
      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation is represented in (\textbf{D}).}
      \label{fig:thresh-maps}
    \end{figure*}

@@

For both group and subject analyses, between-tool variability and machine
error were found to be moderately correlated. Even though between-tool
variability and numerical variability are different in nature, this result
suggests that in some cases both sources of variability may have a common
cause that might be related to the conditioning of the BOLD signal
estimation problem in a specific dataset. Therefore, in some regions,
instabilities of similar magnitude may be triggered by small numerical
perturbations, model variations or implementation differences. For
instance, the analysis of datasets with high motion may be unstable both 
across tools and numerically.

Therefore, numerical stability may be suitable as a proxy to study
between-tool variability. This speculation might be of practical value to
address software variability at large given that numerical stability refers
to a consistent mathematical framework whereas between-tool variability
remains more empirical. Likewise, numerical and between-tool stability may
be interesting proxies for analysis accuracy, and perhaps useful in quality
control.

The finding that numerical variability approached tool variability at the
virtual precision of t=17~bits is interesting too. Indeed, while machine
error generally introduces differences in the order of 1 ulp --- or
t=53~bits for double-precision values and t=24~bits for single-precision
ones --- common scientific software dependencies introduce larger errors.
For instance, SciPy's 2D spline interpolation was recently found to be
precise up to t=10~bits~\cite{pytracer} and might therefore introduce
numerical perturbations leading to errors in the range of between-tool
variability \tristan{Yohan, please check that sentence}. Such high errors
might be triggered by updates in operating systems, Python, MATLAB, and
other software dependencies.

Our results are limited by the type of numerical noise introduced in the
analyses. Indeed, we only introduced noise in the outputs of elementary
mathematical functions while numerical noise could creep in any
floating-point operation. Our estimation of numerical variability should
therefore be considered a lower bound. Our estimation of tool varability is
also likely to be underestimated, having tested only 3 analytical pipelines
among the thousands available~\cite{carp2012plurality}.

@@

Figure~\ref{fig:replication-diff} shows the difference in SPM and AFNI
group analyses maps between the results in~\cite{bowring2019exploring} and
our replication. Numerical perturbations of 1 ulp are likely to have been
introduced by our replication due to the use of Octave vs MATLAB for SPM
and multithreading for AFNI. However, the group maps remained very similar
overall, which led us to conclude that our results correctly reproduced 
the ones in~\cite{bowring2019exploring}.
\begin{figure*}[ht]
  % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  % \centering
  \includegraphics[width=\textwidth]{figures/replication-diffs.png}
  \caption{Differences between reproduced and original results obtained in~\cite{bowring2019exploring} 
  of unthresholded group-level t-statistics for SPM (left) and AFNI (right).}
  \label{fig:replication-diff}
% \end{minipage}}
\end{figure*}

>>>>

We replicated the analysis described as study `ds000001'
in~\cite{schonberg2012decreasing}, relying on the data publicly available
in OpenNeuro at \url{https://openneuro.org/datasets/ds000001} and using
three widely-used software packages for fMRI data processing, namely FMRIB
Software Library (FSL)~\cite{jenkinson2012fsl}, Analysis of Functional
NeuroImages (AFNI)~\cite{cox1996afni}, and Statistical Parametric
Mapping (SPM)~\cite{penny2011statistical}. We selected this dataset because
comparable analysis pipelines implemented in FSL, AFNI and SPM were already 
publicly available and extensively described in~\cite{bowring2019exploring}.
Furthermore, the work in~\cite{bowring2019exploring} already evaluated the
effect of tool variability for this dataset, which we intended to
extend with the present quantification of numerical variability.

In the selected study, 16 healthy adult subjects participated in the
balloon analog risk task~\cite{lejuez2002evaluation} to measure risk-taking
behavior over three scanning sessions~\cite{schonberg2012decreasing}. We
reused the preprocessing, first-level, and second-level analyses
implemented by~\cite{bowring2019exploring} consistently across all three
software packages. Table~\ref{table:pipeline-steps}, adapted from~\cite{bowring2019exploring},
summarizes the analytical steps in each
pipeline.

@@

To introduce numerical noise in the analyses, we used
Fuzzy Libmath~\cite{salari2021accurate}, a version of the GNU
mathematical library (libmath) instrumented with Monte-Carlo arithmetic.
Monte-Carlo arithmetic simulates numerical errors
errors by introducing a controlled amount of noise in floating-point
operations through the following perturbation~\cite{Parker1997-qq}:

@@

Fuzzy Libmath introduces numerical perturbations in the values returned by
mathematical functions but not in their input values or within their
implementation. This is done by wrapping the original functions and
applying function \texttt{inexact} to their returned values.
Listing~\ref{algo:wrapper} shows an example of this wrapping for the
\texttt{log} function in single and double precision. In this wrapper, the
original function is called through \texttt{dlsym}, a function that returns
the memory address of a symbol --- in our case \texttt{RTLD\_NEXT}, the
address of the next occurrence of the function in memory. Compiling function wrappers
with Verificarlo instruments the result of the
addition between the original function output and the floating-point zero.

@@

In~\cite{salari2021accurate}, Fuzzy Libmath was shown to accurately
simulate the effect of Linux operating system updates in structural
pre-processing pipelines of the Human Connectome Project which are largely based on FSL.
 To validate our pipeline instrumentations for the present study, we first verified that non-instrumented
executions of the same pipeline on the same dataset led to identical
results. We also listed the pipeline
library dependencies using the \texttt{ldd} Linux utility and verified that
(1) the tested pipelines were dynamically linked to the GNU libmath library, and 
(2) there was no alternative implementation of elementary mathematical functions in the pipeline dependencies.
Finally, we verified that the use of Fuzzy Libmath affected computational results.

@@

We measured between-tool (BT) variability by running the pipelines
described in~\cite{bowring2019exploring} with FSL version 5.0.10, AFNI
version 18.1.09, and SPM12 version r7771 executed with GNU/Octave version
5.2. These software versions were identical to the study
in~\cite{bowring2019exploring} except for SPM for which we used GNU/Octave
instead of MATLAB to enable mathematical function instrumentation using
Fuzzy Libmath. Indeed, MATLAB uses its own built-in mathematical functions,
which prevents the use of Fuzzy Libmath. In AFNI, we set the number of
threads to 7 even though AFNI executions
in~\cite{bowring2019exploring} were single-threaded. This was meant to
reduce the time overhead resulting from Fuzzy Libmath instrumentation. All
the analyses were conducted on the CentOS 7.3 operating system. The
computations were performed on \href{https://www.computecanada.ca}{Compute
Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake~@~2.4~GHz
 (40 cores/node) CPU and 8~GB of RAM per core. To facilitate portability and reproducibility,
 we encapsulated the
above-mentioned software packages in Docker container images based on CentOS 7.3.

@@

\section{Results}
The scripts, Docker images, and data to reproduce the results are available
in out GitHub repository at
\url{https://github.com/big-data-lab-team/fuzzy-neurotools}.

@@

We verified the correctness of our analyses by comparing our unperturbed
t-statistic group maps with the ones obtained
in~\cite{bowring2019exploring}. For FSL, we found
identical checksums. For SPM, the checksums were different but differences
were visually unnoticeable. For AFNI, the activation maps were similar
overall, however, differences were more noticeable visually. 
The observed differences remained small (see Supplemental Material~\ref{sec:supp-repro}) and might be due to the use of
GNU/Octave vs MATLAB in SPM and of multithreading in AFNI. We performed visual quality control of the AFNI
and SPM results for each individual subject and confirmed that T1-weighted images were
correctly skull-stripped and registered to the MNI template.

@@

Table~\ref{table:pipeline-stats} presents summary statistics for the
group-level t-statistics. For each tool pair (A, B), BT variability was
significantly larger than machine error in tool A or B, in both thresholded
and unthresholded maps (Wilcoxon signed-rank test p~\textless~$10^{-162}$
for all tests, t-test p=0 for all tests).
Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B},\textbf{C} shows that
these global differences were confirmed regionally. 
In addition, BT and WT variability appeared moderately correlated across voxels (Pearson's R
in [0.56, 0.58], p=0.0, Figure~\ref{fig:unthresh-maps}-\textbf{D}). Interestingly, the correlation 
was driven by a set of voxels exhibiting comparable BT and
WT values (located around the identity line in the XY plot), which, however, did not seem to have 
any spatial consistency \tristan{Ali, check for intensity differences between these voxels and the other ones}.

\setlength{\tabcolsep}{5pt}
\begin{table}[h]
    \centering
    \begin{tabular}{cccccc|cc}
        \toprule
        && \multicolumn{4}{c|}{Group map} & \multicolumn{2}{c}{Subject maps}\\
        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded} \\
        % \cmidrule{3-8}
        {} & {} & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ \\
        \midrule
        \rowcolor{lightgray!50}
        {Between Tools} & FSL vs. SPM        &  1.282       & 0.525      & 0.443     & 0.344  & 0.366       & 0.293     \\
        \rowcolor{lightgray!50}
        {(BT)} & FSL vs. AFNI                &  1.548       & 0.616      & 0.547     & 0.441  & 0.439       & 0.352     \\
        \rowcolor{lightgray!50} 
        {} & AFNI vs. SPM                    &  1.475       & 0.672      & 0.608     & 0.477  & 0.491       & 0.381     \\
        {Within Tool} & FSL                  &  0.354       & 0.491      & 0.082     & 0.065  & 0.077       & 0.054     \\
        {(WT)}   & SPM                       &  0.252       & 0.448      & 0.054     & 0.045  & 0.048       & 0.037     \\
        {}   & AFNI                          &  0.434       & 0.524      & 0.128     & 0.135  & 0.108       & 0.131     \\
        \bottomrule
    \end{tabular}
    \caption{Voxel-wise mean and standard deviation of BT and WT variability
    in t-statistics maps. \tristan{add stats on subject-level thresholded maps}}
    \label{table:pipeline-stats}
\end{table}

@@

  Table~\ref{table:pipeline-stats} also presents summary statistics for
  subject-level unthresholded t-statistics maps. As for group-level maps,
  BT variability was consistently larger than WT variability (Wilcoxon
  signed-rank test p~\textless~$10^{-160}$ for all tests, t-test p=0 for
  all tests). However, Figure~\ref{fig:unthresh-maps-sbj} shows that for
  some subjects, machine error (WT variability) approached and even
  surpassed BT in some regions. As for the group maps, BT and WT
  variability appeared moderately correlated for all subjects (R in [0.442,
  0.612], p=0.0 for all subjects, see Supplemental Material~\ref{sec:supp-subjects}).

@@

  Figure~\ref{fig:thresh-maps}-\textbf{A},\textbf{B},\textbf{C} compares BT
  and WT for thresholded group maps. Thresholding is an unstable operation
  that introduced variability at the edges of
  active regions for both BT and WT. Except in these regions, BT remained consistently larger
  than WT. Moreover, to measure correlation between BT and WT, we
  measured WT instability and BT instability in each region of the
  HCP-MMP1.0 parcellation. The confusion matrices in
  Figure~\ref{fig:thresh-maps}-\textbf{D} report these instabilities for
  the 360 tested regions. The average ratio of unstable regions was 26\%
  for BT and 9.2\% for WT, which confirmed that BT variability was larger than machine error.
  The average Cohen's kappa score\footnote{$\kappa \leq 0$ denotes chance agreement, $-1 \leq \kappa \leq 1$}
   between WT instability and BT instability was $\kappa=0.17$, indicating 
  a moderate agreement between WT instability and BT instability.

  %%%%%%%%%% Var. of Thresh %%%%%%%%
  \begin{figure*}[ht]
        \begin{subfigure}[ht]{\textwidth}
          \centering
          \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
          %\caption{Standard deviation of thresholded t-statistics map on template surface}
          \end{subfigure}
        \centering
      \caption{Thresholded group t-statistics standard deviations computed between tools (\textbf{A}),
      within tools at the virtual precision of t=17~bits (\textbf{B}), difference between them (\textbf{C}), and 
      confusion matrices of activation instability
      in BT and WT among the 360 regions of the HCP-MMP1.0 parcellation (\textbf{D}).}
      \label{fig:thresh-maps}
    \end{figure*}

@@

For both group and subject analyses, between-tool variability and machine
error were found to be moderately correlated. Even though between-tool
variability and numerical variability are different in nature, this result
suggests that in some cases both sources of variability may have a common
cause that might be related to the conditioning of the BOLD signal
estimation problem in a specific dataset. Therefore, in some regions,
instabilities of similar magnitude may be triggered by small numerical
perturbations, model variations, or implementation differences. For
instance, the analysis of datasets with high motion may be unstable both 
across tools and numerically.

Therefore, numerical stability may be a suitable proxy to study
between-tool variability. This speculation might be of practical value to
address software variability at large given that numerical stability refers
to a consistent mathematical framework whereas between-tool variability
remains more empirical. Likewise, useful quality control metrics may be derived from numerical and between-tool stability.

The finding that numerical variability approached tool variability at the
virtual precision of t=17~bits is interesting too. Indeed, while machine
error generally introduces differences in the order of 1 ulp --- or
t=53~bits for double-precision values and t=24~bits for single-precision
ones --- common scientific software dependencies introduce larger errors.
For instance, SciPy's 2D spline interpolation was recently found to be
precise up to t=10~bits~\cite{pytracer} \tristan{Fix ref} and might therefore introduce
numerical perturbations leading to errors in the range of between-tool
variability \tristan{Yohan, please check that sentence}. Such high errors
might be triggered by updates in operating systems, Python, MATLAB, and
other software dependencies.

Our results are limited by the type of numerical noise introduced in the
analyses. We only perturbed the outputs of elementary
mathematical functions while numerical noise could creep in any
floating-point operation. Our estimation of numerical variability should
therefore be considered a lower bound. Our estimation of tool varability is
also likely to be underestimated, having tested only 3 analytical pipelines
among the thousands available~\cite{carp2012plurality}.

@@

Figure~\ref{fig:replication-diff} shows the difference in SPM and AFNI
group analyses maps between the results in~\cite{bowring2019exploring} and
our replication. Numerical perturbations of 1 ulp are likely to have been
introduced by our replication due to the use of GNU/Octave vs MATLAB for SPM
and multithreading for AFNI. However, the group maps remained very similar
overall, which led us to conclude that our results correctly reproduced 
the ones in~\cite{bowring2019exploring}.
\begin{figure*}[ht]
  % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  % \centering
  \includegraphics[width=\textwidth]{figures/replication-diffs.png}
  \caption{Differences between reproduced and original results obtained in~\cite{bowring2019exploring} 
  of unthresholded group-level t-statistics for SPM (left) and AFNI (right).}
  \label{fig:replication-diff}
% \end{minipage}}
\end{figure*}
